paper

### 2019-01-10 Report/paper.tex
push change

\renewcommand{\figurename}{Figure}
\captionsetup{labelformat=simple}\title{Bibliometric Analysis of ICLS and CSCL research}
\author{\IEEEauthorblockN{Léonore Valentine Guillain, Nour Ghalia Abassi}\par
    \IEEEauthorblockA{EPFL}
}
\maketitle

@@

\begin{itemize}
\tightlist
\item
  the institutions and countries dominant in the conferences
\item
  the differences between ICLS and CSCL with respect to citations,
  contributors and publications
\item
  first insight into changes of the years with respect to citations,
  contributors and publications
\item
  collaboration network patterns with respect to countries, institutions
  and authors
\item
  the migration of participants across institutions
\item
  trends of keywords over the years
\item
  trends of citations and evolution of the number of documents from 1977
  until 2018
\item
  clusters of the cited documents
\item
  clusters of the papers written within the conferences
\end{itemize}

>>>>

\renewcommand{\figurename}{Figure}
\captionsetup{labelformat=simple}\title{   }
\author{
}
\maketitle

@@

\begin{itemize}
\tightlist
\item
  The institutions and countries dominant in the conferences
\item
  The differences between ICLS and CSCL with respect to citations,
  contributors and publications
\item
  First insight into changes of the years with respect to citations,
  contributors and publications
\item
  Collaboration network patterns with respect to countries, institutions
  and authors
\item
  The migration of participants across institutions
\item
  Trends of keywords over the years
\item
  Trends of citations and evolution of the number of documents from 1977
  until 2018
\item
  Clusters of the cited documents
\item
  Clusters of the papers written within the conferences
\end{itemize}
